The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-06-12 paper.tex
Update author information and acknowledgement.

% For one author:
%\author{\inits{N.}\fnms{Name1} \snm{Surname1}\ead[label=e1]{first@somewhere.com}}
%\address{Department first, \orgname{University or Company name},
%Abbreviate US states, \cny{Country}\printead[presep={\\}]{e1}}
% Höffner, Heuschkel, Schmiedel, Penne, Fritzsch, Ludwig, Mohaupt, Labudde, Uciteli
% TODO: overleaf
% Two or more authors:
\begin{aug}
\author[B]{\inits{M.}\fnms{Marie} \snm{Heuschkel}\ead[label=e2]{marie.heuschkel@hs-mittweida.de}}
\author[A]{\inits{K.}\fnms{Konrad} \snm{Höffner}\ead[label=e1]{konrad.hoeffner@uni-leipzig.de}%
\thanks{Corresponding author. \printead{e1}.}
\thanks{Equal contribution.}%how to show this for the first 3?
}
\author[B]{\inits{F.}\fnms{Fabian} \snm{Schmiedel}\ead[label=e3]{fabian.schmiedel@hs-mittweida.de}}
\author[B]{\inits{L.}\fnms{Laura} \snm{Penne}\ead[label=e4]{laura.penne@hs-mittweida.de}}
\author[B]{\inits{H. T.}\fnms{Hanjo Tim} \snm{Fritzsch}\ead[label=e5]{fritzsc2@hs-mittweida.de}}
\author[B]{\inits{N.}\fnms{Niklas} \snm{de Sousa Norte}\ead[label=e6]{niklas.desousanorte@hs-mittweida.de}}
\author[B]{\inits{A.}\fnms{Andrea} \snm{Ferencová}\ead[label=e7]{andrea.ferencova@hs-mittweida.de}}
\author[B]{\inits{A.}\fnms{Andy} \snm{Ludwig}\ead[label=e8]{andy.ludwig@hs-mittweida.de}}% ist jetzt beim Fraunhofer, möchte aber weiter so gelistet werden
\author[B]{\inits{M.}\fnms{Marleen} \snm{Mohaupt}\ead[label=e9]{kreuzer@hs-mittweida.de}}
\author[B]{\inits{D.}\fnms{Dirk} \snm{Labudde}\ead[label=e10]{dirk.labudde@hs-mittweida.de }}
\author[A]{\inits{A.}\fnms{Alexandr} \snm{Uciteli}\ead[label=e11]{alexander.uciteli@imise.uni-leipzig.de}}
%\author[B]{\inits{}\fnms{} \snm{}\ead[label=e9]{}}
\address[A]{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), \orgname{Leipzig University},
Saxony, \cny{Germany}\printead[presep={\\}]{e1,e11}}
\address[B]{\orgname{Hochschule Mittweida},
Saxony, \cny{Germany}\printead[presep={\\}]{e2,e3,e4,e5,e6,e7,e8,e9,e10}}
\end{aug}

@@

\begin{ack}
\noindent\begin{minipage}{0.90\textwidth}
The ANNO project is co-financed from tax funds based on the budget passed by the Parliament of the Free State of Saxony.
\end{minipage}%
\hfill%
\begin{minipage}{0.04\textwidth}\raggedleft
\includegraphics[width=\textwidth]{img/saxony.pdf}
\end{minipage}
\end{ack}

>>>>

% For one author:
%\author{\inits{N.}\fnms{Name1} \snm{Surname1}\ead[label=e1]{first@somewhere.com}}
%\address{Department first, \orgname{University or Company name},
%Abbreviate US states, \cny{Country}\printead[presep={\\}]{e1}}
% Höffner, Heuschkel, Schmiedel, Penne, Fritzsch, Ludwig, Mohaupt, Labudde, Uciteli
% TODO: overleaf
% Two or more authors:
\begin{aug}
\author[B]{\inits{M.}\fnms{Marie} \snm{Heuschkel}\ead[label=e2]{marie.heuschkel@hs-mittweida.de}}
\author[A]{\inits{K.}\fnms{Konrad} \snm{Höffner}\ead[label=e1]{konrad.hoeffner@uni-leipzig.de}%
\thanks{Corresponding author. \printead{e1}.}
\thanks{Equal contribution.}%how to show this for the first 3?
}
\author[B]{\inits{F.}\fnms{Fabian} \snm{Schmiedel}\ead[label=e3]{fabian.schmiedel@hs-mittweida.de}}
\author[B]{\inits{D.}\fnms{Dirk} \snm{Labudde}\ead[label=e10]{dirk.labudde@hs-mittweida.de }}
\author[A]{\inits{A.}\fnms{Alexandr} \snm{Uciteli}\ead[label=e11]{alexander.uciteli@imise.uni-leipzig.de}}
%\author[B]{\inits{}\fnms{} \snm{}\ead[label=e9]{}}
\address[A]{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), \orgname{Leipzig University},
Saxony, \cny{Germany}\printead[presep={\\}]{e1,e11}}
\address[B]{\orgname{Hochschule Mittweida},
Saxony, \cny{Germany}\printead[presep={\\}]{e2,e3,e10}}
\end{aug}

@@

\begin{ack}
\noindent\begin{minipage}{0.90\textwidth}
We gratefully acknowledge Laura Penne for her valuable support in data acquisition and the conception and design of the input format.
We would like to express our sincere thanks to Andrea Ferencová and Hanjo Tim Fritzsch for their contributions to data acquisition.
Additionally, we extend our gratitude to Marleen Mohaupt, Andy Ludwig and Niklas de Sousa Norte for their contributions to data acquisition and project support.
The ANNO project is co-financed from tax funds based on the budget passed by the Parliament of the Free State of Saxony.

%\author[B]{\inits{L.}\fnms{Laura} \snm{Penne}\ead[label=e4]{laura.penne@hs-mittweida.de}}
%\author[B]{\inits{A.}\fnms{Andrea} \snm{Ferencová}\ead[label=e7]{andrea.ferencova@hs-mittweida.de}}
%\author[B]{\inits{N.}\fnms{Niklas} \snm{de Sousa Norte}\ead[label=e6]{niklas.desousanorte@hs-mittweida.de}}
%\author[B]{\inits{H. T.}\fnms{Hanjo Tim} \snm{Fritzsch}\ead[label=e5]{fritzsc2@hs-mittweida.de}}
%\author[B]{\inits{A.}\fnms{Andy} \snm{Ludwig}\ead[label=e8]{andy.ludwig@hs-mittweida.de}}% ist jetzt beim Fraunhofer, möchte aber weiter so gelistet werden
%\author[B]{\inits{M.}\fnms{Marleen} \snm{Mohaupt}\ead[label=e9]{kreuzer@hs-mittweida.de}}
\end{minipage}%
\hfill%
\begin{minipage}{0.04\textwidth}\raggedleft
\includegraphics[width=\textwidth]{img/saxony.pdf}
\end{minipage}
\end{ack}
